Charity analysis

### 2022-07-20 Shiny/Test/Flexdashboard rows.Rmd
Testing themes.

---
title: "Charity analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using fontawesome for more up-to-date fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

  # Creating the value box for administrative expenses
  output$KPI_box <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

@@

  # Creating fancy plotly output
  output$CEO_plotly <- renderPlotly(
    ggplotly(CEO_plot())
  )

>>>>

---
title: "Charity analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: lumen
runtime: shiny
---

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using fontawesome for more up-to-date fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())

# Considering lumen or cerulean theme
```

@@

  # Creating the value box for administrative expenses
  output$KPI_box <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Troy", n = 1),
      icon = "fa-random"
    )
  })

@@

  # Creating plotly output
  output$CEO_plotly <- renderPlotly(
    ggplotly(CEO_plot())
  )
